Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-02-06 manuscript/bef_stability/manuscript.Rmd
residual plot sem

```{r, eval = FALSE}
compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)

@@

tibble(
  vif = colin_stab_sem,
  mod = names(mod_list)
) 
test <- cbind(colin_stab_sem)

formulas <- list(
  "log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
  "piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
)
test <- map(formulas, function(x, y, random_effect) {
  lmer(as.formula(x), random= as.formula(random_effect), data = y)

}, y =sem_data, random_effect = "~ 1 |basin")

>>>>

```{r colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}
#compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)

@@

tmp <- map(colin_stab_sem, enframe)

# colinearity table
colin_sem <- tibble(vif = tmp, mod = names(mod_list)) %>%
  unnest(vif) %>%
  spread(name, value)

#formulas <- list(
  #"log_rich ~ RC1 + RC2 + RC3 + RC4 + RC5",
  #"piel ~ RC1 + RC2 + RC3 + RC4 + RC5"
#)
#test <- map(formulas, function(x, y, random_effect) {
  #lmer(as.formula(x), random= as.formula(random_effect), data = y)

#}, y =sem_data, random_effect = "~ 1 |basin")

kable(colin_sem)
```

```{r}
plot_residuals <- function (x, y = "Diagnostic") {
  plot.lme(x)
  #title(main = y, xlab = "Fitted values", y = "Residuals")
}
plot.lme(mod_list[[7]])
p_resid_stab_sem <- map2(mod_list, names(mod_list) , plot_residuals)
plot_grid(plotlist = p_resid_stab_sem)
```
